\huge Tor's Usability for Censorship Circumvention

### 2016-05-09 pets2017-paper/pets2017-paper.tex
Spell check.

Users found the feedback to be more confusing than helpful, since error messages were technical and progress bar was misleading. We make the following changes to make feedback insightful and reflective of system state:\\ 
\begin{enumerate}
\setcounter{enumi}{3}
\item Progress bar feedback is accurate.  We fixed the bug that caused the progress bar to not update on subsequent attempts. What users now see on the progress bar reflects the reality of the progress. 
\item Made the interface text less technical. We made the text more task-centric by focusing on instructing users through the configuration process. Since users generally did not understand the technical concepts sufficiently to influence their decisions, we thibk giving direct guidance is a better option. 
\item Added system status visibility. Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings. The same information is shown on the progress screen while the connection is in progress. We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
\end{enumerate}

>>>>

Users found the feedback to be more confusing than helpful, since error messages were technical and progress bar was misleading. We make the following changes to make feedback insightful and reflective of system state:\\ 
\begin{enumerate}
\setcounter{enumi}{3}
\item Progress bar feedback is accurate.  We fixed the bug that caused the progress bar to not update on subsequent attempts. What users now see on the progress bar reflects the reality of the progress. 
\item Made the interface text less technical. We made the text more task-centric by focusing on instructing users through the configuration process. Since users generally did not understand the technical concepts sufficiently to influence their decisions, we think giving direct guidance is a better option. 
\item Added system status visibility. Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings. The same information is shown on the progress screen while the connection is in progress. We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
\end{enumerate}
